Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-03-06 supCLT.tex
supCLT.tex: 0303
0305

% supCLT0128.tex 2018/01/28 by Renming
% supCLT0127.tex 2018/01/27 by Yanxia
% supCLT0124.tex 2018/01/24 by Jianjie
% supCLT0114.tex 2018/01/14 by Yanxia
% supCLT0107.tex 2018/01/07 by Jianjie

@@

%\usepackage[backref=section]{hyperref}
\usepackage{hyperref}

@@

    [CLT for Super-OU processes]
    {Stable Central Limit Theorems for Super OU Processes with Stable Branching}

@@

\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}

@@

@@

    Consider a super Ornstein-Uhlenbeck processes (super-OU process) $(X_t)_{t\geq 0}$ with branching mechanism $\psi(z)=-\alpha z +\eta z^{1+\beta} + \psi_1(z),$ where $\alpha >0$ and $\beta\in (0,1)$ and $psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that $|\psi_1(z)| \leq C(|z|^2+|z|^{1+\gamma + \delta}).$
    For each testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$.
    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
    In the small branching rate case $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly to a $(1+\beta)$-stable random variable.
    In the critical branching rate case  $\alpha\beta= \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly another $(1+\beta)$-stable random variable.
    In the large branching rate case  $\alpha\beta> \kappa_f b(1+\beta)$, we first prove that $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$, and then established a central limit theorem, which says that, after proper centering and scaling, $\langle f,X_t\rangle$ again converges weakly to a $(1+\beta)$-stable random variable.

@@

%\subjclass[2010]{60J80, 60F05}
%\keywords{}

@@

%Moved and modified from below

@@

In this paper, we will establish some spatial central limit theorems for the super-OU process above. Precisely, we want to find $F_t$ and $G_t$ such that
    \frac{\langle f, X_t \rangle -G_t}{F_t}
    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for some test functions $f$. 
    It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.

    There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses. 
    See \cite{KestenStigum1966A-limit,KestenStigum1966Additional} for supercritical multi-type Galton-Waston processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions. 
    In \cite{AdamczakMilos2015CLT}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition. 
    These two papers made connections between CLT and what they call branching rate regimes. 
    In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment. 
    Moverover, compared with the results in \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate. 
    In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central,RenSongZhang2017Functional}, Ren, Song and Zhang also established a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.
    All the results described above hold for systems with branching mechanisms with finite variance. 
    It is natural to ask whether there are counterparts of the central limit theorems for branching Markov processes and superprocesses with branching mechanisms of infinite variance.
    In \cite{MarksMilos2018CLT}, Marks and Milo\'s considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law. They established some central limit theorems in small and critical branching rate cases, but \cite{MarksMilos2018CLT} contained no central limit result in the branching rate case.
    In this paper, we consider a class of super-OU processes with more general stable branching mechanisms. 
    For small and critical branching rate cases, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MarksMilos2018CLT}. 
    For large branching rate case, we first establish  an almost sure convergence result, and then establish a central limit theorem, which has no counterpart in \cite{MarksMilos2018CLT}.

%Added
    {\bf ZS: I think this subsection should be extended with more literatures like: 
    \cite{AdamczakMilos2014U-statistics}, 
    \cite{EckhoffKyprianouWinkel2015Spines},
    \cite{EnglanderHarrisKyprianou2010Strong},
    \cite{IksanovKabluchko2016A-central}, 
    \cite{LiuRenSong2013Strong}, 
    \cite{Wang2018Central},
    \cite{IksanovKoleskoMeiners2018Stable-like},
    \cite{IksanovKoleskoMeiners2018Fluctuations},
    \cite{GrubelKabluchko2016A-functional},
    \cite{Heyde1970A-rate}, 
    \cite{Heyde1971Some}, 
    \cite{HeydeBrown1871An-invariance}, 
    \cite{HeydeLeslie1971Improved}, 
    \cite{BansayeDelmasMarsalleTran2011Limit}, 
    \cite{EnglanderWinter2006Law}, 
    \cite{Englander2009Law}, 
    \cite{Janson2004Functional}, 
    \cite{ChenRenWang2008An-almost}, 
    \cite{Wang2010An-almost}, 
    \cite{HartungKlimovsky2018The-phase}, 
    \cite{BansayeDelmasMarsalleTran2011Limit}, 
    \cite{Le2019Long}.
}
%end and modified from below
%\subsection{Model}\label{sec: main results}
\subsection{Main results}
\label{sec: main results}{}
	Let $d \in \mathbb N:= \{1,2,\dots\}$.
%moved and modifeid from below 
    Let $\mathbb R_+:= [0,\infty)$.
    Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel measurable functions on $\mathbb R^d$.
    Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel measurable functions on $\mathbb R^d$.
    For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integral makes sense.
    For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
%deletd
    %Write $\|\mu\|=\langle 1,\mu\rangle$ for each $\mu \in \mathcal M(\mathbb R^d)$. 
%end deleted
%end moved from below

@@

    where $\sigma$ and $b$ are positive constants.
%deleted
    %Denote by $(P_t)_{t\geq 0}$ the transition semigroup of $\xi$.
%end deleted
    %Let $\psi$ be the function on $\mathbb R_+$ defined by

@@

	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}y\wedge y^2 \pi(dy)< \infty$.
%new added
	It is known that $\alpha, \rho$ and $\pi$ are uniquelly determined by function $\psi$. 

@@

%end new added
%moved above
    %We use $\mathcal B(\mathbb R^d, \mathbb R)$ to denote   the space of all real-valued Borel measurable functions on $\mathbb R^d$ and use $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
	%For $f\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, we write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
    %We aslo use the notation $\|\mu\|=\langle 1,\mu\rangle$. 
    %For $f, g\in \mathcal B(\mathbb R^d, \mathbb R)$, we also write $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integral makes sense.
%end moved above
    %We say an $\mathcal M(\mathbb R^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
    We say an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have

@@

%\label{super}

@@

%\label{eq1}
	%V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(\xi_s,V_{t-s}f(\xi_s)\big)~ds\Big]

@@

    %The existence of superprocesses is well known, see \cite{Dynkin1993Superprocesses} for instance.

@@

%Added

	Denote by $\Gamma$ the gamma function. 
	In this paper, we will always assume that the following Assumption holds.
%End added

%Deleted
    %According to Subsection A.1, the branching mechanism $\psi$ can be extended to
    %$\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$ by
 %\[
    %\psi(z)=
    %- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
    %\quad  z \in \mathbb C_+,
%\]
    %which is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
    %\{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
%\begin{equation}
%\label{eq: deriavetive of the Poission part}
    %\psi'(z) := -\alpha + 2\rho z+ \int_{(0,\infty)} (1-e^{-zy}) y\pi(dy),
    %\quad z\in \mathbb C^0_+.
%\end{equation}

%\begin{asp}
%\label{asp: branching mechanism}
    %The branching mechanism takes the form of
%\[
    %\psi(z) = -\alpha z + \eta z^{1+\beta} + \psi_1(z),\quad z\in \mathbb C_+,
%\]
    %where $\alpha>0$, $\eta > 0$, $\beta \in (0,1)$ and $\psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that
%\[
    %|\psi_1(z)| \leq C(|z|^2+|z|^{1+\beta + \delta}),\quad z\in \mathbb C_+.
%\]
%\end{asp}
%end Deleted
%added
\begin{asp}
\label{asp: branching mechanism}
    There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
\begin{equation}
\label{eq: asp of branching mechanism}
    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty,
\end{equation}
	for some $\delta > 0$.
\end{asp}

	It will be showed in Subsection \ref{sec: branching mechanism} that if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquelly determined by the L\'evy measure $\pi$.
	In the reminder of the paper, we will always write $\eta,\beta$ for the constants corresponding to $\pi$.
\begin{rem}
\label{rem: small enough delta}
	Note that $\delta$ is not uniquelly determined by $\pi$. 
	In fact, if $\delta>0$ is a constant such that \eqref{eq: asp of branching mechanism} holds, then replacing $\delta$ by any smaller positive number, \eqref{eq: asp of branching mechanism} still holds.
	Therefore, Assumption \ref{asp: branching mechanism} is equivalent to the following statements: There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that, for each small enough $\delta>0$, \eqref{eq: asp of branching mechanism} holds.
\end{rem}

    Assumption \ref{asp: branching mechanism} says that there exists a constatn $\eta>0$ and $\beta > 0$ such that the Levy measure $\pi(dy)$ is not too far away from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$. 
    In particular, if $\pi(dy)$ equals to $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$, then the branching mechanism $\psi(z)$ takes the form of a stable branching
	$-\alpha z + \rho z^2 + \eta z^{1+\beta}$.
	It will be proved in Lemma \ref{lem: LlogL criterion} that under Assumption \ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the $L \log L$ criteria, i.e. 
\[
	\int_{(1,\infty)} y\log y~\pi(dy) < \infty.
\]

	In this paper, we will also assume the following:
\begin{asp}
\label{asp: Greys condition}
	The branching mechanism satisfies the Grey's condition, i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
\end{asp}
%end added
%moved to the nexe section
%\begin{lem}
    %Under Assumption \ref{asp: branching mechanism}, we have that $\psi$ satisfies the Grey's condition i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
    %Also, $\psi$ satisfies the $L \log L$ criterion  i.e.,
%\[
    %\int_1^\infty y \log y~\pi(dr)< \infty.
%\]
%\end{lem}
%\begin{proof}
    %{ Need a proof.}
%\end{proof}
%end moved to the next section

%Deleted
    %According to \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations}, we have
%\begin{equation}
    %\mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
    %= e^{-\bar v \|\mu\|},
%\end{equation}
    %where $\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
%End Deleted
%Added
	It is known (see \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations} for example) that, under Assumption \ref{asp: Greys condition}, the \emph{distinguish event} $D:=\{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ has a positive probability, with respect to each $\mathbb P_\mu$ with $\mu \in \mathcal M(\mathbb R^d)$.
    In fact,
\begin{equation}
    \mathbb{P}_{\mu} (D)
    = e^{-\bar v \|\mu\|},
    \quad \mu\in \mathcal M(\mathbb R^d),
\end{equation}
    where 
\[
	\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\} \in (0,\infty)
\]
	is the largest root of $\psi$.
%End added

	Define
\label{eq: meansemigroup}
    P^{\alpha}_t f(x)
    :=
    e^{\alpha t} P_t f(x) =
    \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
%\label{eq:meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle P^\alpha_t f, \mu \rangle,
    \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
%Moved to the first Subsection
    %In this paper, we will establish some spatial central limit theorems for the super-OU process above. Precisely, we want to find $F_t$ and $G_t$ such that
    %\frac{\langle f, X_t \rangle -G_t}{F_t}
    %converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for some test functions $f$. 
    %It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
    %There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses. 
    %See \cite{KestenStigum1966A-limit,KestenStigum1966Additional} for supercritical multi-type Galton-Waston processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions. 
    %In \cite{AdamczakMilos2015CLT}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition. 
    %These two papers made connections between CLT and what they call branching rate regimes. 
    %In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment. 
    %Moverover, compared with the results in \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate. 
    %In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central,RenSongZhang2017Functional}, Ren, Song and Zhang also established a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.
    %All the results described above hold for systems with branching mechanisms with finite variance. 
    %It is natural to ask whether there are counterparts of the central limit theorems for branching Markov processes and superprocesses with branching mechanisms of infinite variance.
    %In \cite{MarksMilos2018CLT}, Marks and Milo\'s considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law. They established some central limit theorems in small and critical branching rate cases, but \cite{MarksMilos2018CLT} contained no central limit result in the branching rate case.
    %In this paper, we consider a class of super-OU processes with more general stable branching mechanisms. 
    %For small and critical branching rate cases, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MarksMilos2018CLT}. 
    %For large branching rate case, we first establish  an almost sure convergence result, and then establish a central limit theorem, which has no counterpart in \cite{MarksMilos2018CLT}.
%End moved to the first subsection

>>>>

% supclt0220.tex 2019/02/20 by Jianjie
% supclt0217.tex 2019/02/14 by Renming
% supclt0214.tex 2019/02/14 by Yanxia
% supclt0211.tex 2019/02/11 by Zhenyao
% supCLT0128.tex 2019/01/28 by Renming
% supCLT0127.tex 2019/01/27 by Yanxia
% supCLT0124.tex 2019/01/24 by Jianjie
% supCLT0114.tex 2019/01/14 by Yanxia
% supCLT0107.tex 2019/01/07 by Jianjie

@@

\usepackage[backref=section]{hyperref}
%\usepackage{hyperref}

@@

    %[CLT for Super-OU processes]
    [stable CLT for super-OU processes]
    %{Stable Central Limit Theorems for Super OU Processes with Stable Branching}
    {Stable Central Limit Theorems for Super Ornstein-Uhlenbeck Processes}

@@

\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009) and LMEQF.}

@@

\thanks{Jianjie Zhao is the corresponding author}
%ZS: I changed all "branching rate regime" to "branching rate regime" below.

@@

	%Consider a super Ornstein-Uhlenbeck processes (super-OU process) $(X_t)_{t\geq 0}$ with branching mechanism 
    Consider a $(\xi, \psi)$-superprocess $(X_t)_{t\geq 0}$ where the spatial motion $\xi$ is an Ornstein-Uhlenbeck process on $\mathbb R^d$  which has generator $L = \frac{1}{2}\sigma^2\Delta - b x \cdot \nabla$ with $\sigma, b >0$, and the
    branching mechanism $\psi$ takes the form close to
	$\psi(z)=-\alpha z +\rho z^2+ \eta z^{1+\beta}$ with $\alpha>0$, $\rho\ge 0$, $\eta>0$ and $\beta\in (0, 1)$ in some sense.
    For any testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the mean semigroup of $X$.
    %Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes: 
    Conditioned on non-extinction, we establish some stable central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
    %In the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly to a $(1+\beta)$-stable random variable.
    %In the critical branching rate regime  $\alpha\beta= \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly another $(1+\beta)$-stable random variable.
    %In the large branching rate regime  $\alpha\beta> \kappa_f b(1+\beta)$, we first prove that $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$, and then established a central limit theorem, which says that, after proper centering and scaling, $\langle f,X_t\rangle$ again converges weakly to a $(1+\beta)$-stable random variable.
    the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$.

@@

\subjclass[2010]{60J68, 60F05}
\keywords{Superprocesses, Ornstein-Uhlenbeck processes, Stable distribution, Central limit theorem, Law of large numbers, Branching rate regime}

@@

@@

	Let $d \in \mathbb N:= \{1,2,\dots\}$ and $\mathbb R_+:= [0,\infty)$.
%MOVED BELOW
    %Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel measurable functions on $\mathbb R^d$.
    %Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel measurable functions on $\mathbb R^d$.
    %Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
    %For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
    %For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
    %We say a real-valued measurable function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if for each $t\in \mathbb R_+$, we have
    %\sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
%END MOVED BELOW

@@

    %where $\sigma$ and $b$ are positive constants.
    where $\sigma > 0$ and $b > 0$ are constants.

@@

	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}(y\wedge y^2) \pi(dy)< \infty$.
%DELETED
	%It is known that $\alpha, \rho$ and $\pi$ are uniquely determined by the function $\psi$.
%END DELETED

@@

%MOVED FROM ABOVE
    For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integrals make sense.
%END MOVED FROM ABOVE
       We say an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ 
on a measurable space $(\Omega, \mathcal{F})$       
       is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have

@@

\label{eq: def of V_t}

@@

@@

@@

    Recently, there have been quite a few papers on laws of large numbers for superdiffusions. In \cite{Englander2009Law, EnglanderWinter2006Law, EnglanderTuraev2002A-scaling}, some weak laws of large numbers (convergence in law or in probability) were established. The strong law of large numbers for superprocesses was first studied in \cite{ChenRenWang2008An-almost}, 
    %followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines,KouritzinRen2014A-strong,LiuRenSong2013Strong, Wang2010An-almost}. 
    %The setups of the papers mentioned above are  different. 
    followed by \cite{ChenRenSongZhang2015Strong-law, ChenRenYang2019Skeleton, EckhoffKyprianouWinkel2015Spines,KouritzinRen2014A-strong,LiuRenSong2013Strong, Wang2010An-almost} under different settings. 
    For a good survey on recent developments in laws of large numbers for branching Markov processes and superprocesses, see \cite{EckhoffKyprianouWinkel2015Spines}.

    %In this paper, we focus on limit results for the super-OU process $X$.
    %The strong law of large numbers of $X$ can be stated as follows: 
    The strong law of large numbers of the above super-OU process $X$ can be stated as follows: 
    Under some conditions on the branching mechanism $\psi$ (these conditions are satisfied under our assumptions 1 and 2, below), there exists an $\Omega_0$ of $\mathbb{P}_\mu$-full probability for every $\mu\in\mathcal M(\mathbb R^d)$ such that on $\Omega_0$, 
    %for every Lebesgue-almost everywhere continuous bounded $f\in\mathcal B(\mathbb R^d, \mathbb R_+)$,
    for every Lebesgue-almost everywhere continuous bounded non-negative function $f$ on $\mathbb R^d$, 
    we have
    $\lim_{t\to\infty}e^{-\alpha t}\langle f, X_t\rangle=H_\infty\langle f,\phi_0\varphi\rangle $, 
    %where  $H_\infty=\lim_{t\to\infty}e^{-\alpha t}\|X_t\|$, and the convergence also holds in $L^1(\mathbb P_\mu)$, see \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.
    where $H_\infty$ is the limit of the non-negative martingale $e^{-\alpha t}\langle 1,X_t\rangle$ and $\phi_0$, $\varphi$ are functions which will be introduced in  \eqref{eigenfunction} and \eqref{invariantdensity} below.
    See \cite[Theorem 2.13 \& Example 8.1]{ChenRenYang2019Skeleton} and \cite[Theorem 1.2 \& Example 4.1]{EckhoffKyprianouWinkel2015Spines}.

    %In this paper, we will establish some spatial central limit theorems for the super-OU process $X$ above.  
    In this paper, we will establish some spatial central limit theorems (CLT) for the super-OU process $X$ above. 
%NEW ADDED
    Our key assumption is that the corresponding branching mechanism $\psi(z)$ takes the form of $-\alpha z +\rho z^2+ \psi_1(z)$ where $\psi_1$ is close to $\eta z^{1+\beta}$ with $\eta>0$ and $\beta\in (0, 1)$ in some sense.
%END ADDED
    %More precisely, we want to find 
    We want to find
    %$F_t$ and $G_t$ such that
    $(F_t)_{t\geq 0}$ and $(G_t)_{t\geq 0}$ such that
\[
    \frac{\langle f, X_t \rangle -G_t}{F_t}
\]
    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, 
    %for some test functions $f$.
    for some testing functions $f$.
    %It turns out that the normalization $F_t$ depends on the branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.
    It turns out that there are three regimes of different behavior of this CLT depending on the sign of $\alpha\beta-\kappa_f b (1+\beta)$: the small branching rate regime $\alpha\beta< \kappa_f b(1+\beta)$; the critical branching rate regime $\alpha\beta = \kappa_f b(1+\beta)$; and the large branching rate regime $\alpha\beta > \kappa_f b(1+\beta)$. Here, $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$. 
%ADDED
    Note that, under the settings of this paper, $\langle f,X_t\rangle$ typically have infinite second moment.
%END ADDED

    %There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses.
    There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses under finite second moment condition.
    See
    \cite{Heyde1970A-rate, HeydeBrown1871An-invariance, HeydeLeslie1971Improved} for supercritical Galton-Watson processes, 
    %see \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type Galton-Waston processes, 
    \cite{KestenStigum1966Additional,KestenStigum1966A-limit} for supercritical multi-type Galton-Watson processes,
    \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions.
    In \cite{AdamczakMilos2015CLT}, 
    %Adamcazk and Milo\'s 
    Adamczak and Milo\'s 
    proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition.
    These two papers made connections between CLT and what they call branching rate regimes.
    In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying only a second moment.
    %Moverover, 
    Moreover,
    compared with the results in \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate.
    In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central},
    Ren, Song and Zhang also established a series of central limit theorems for a large class of general supercritical branching Markov processes and superprocesses with spatially dependent branching mechanisms.
    The functional version of the central limit theorems was established in \cite{Janson2004Functional} for supercritical multitype branching processes, and  in \cite{RenSongZhang2017Functional} for supercritical superprocesses.

    %All central limit results described above hold for systems with branching mechanisms with finite variance.
    %It is natural to ask whether there are counterparts of the central limit theorems for branching Markov processes and superprocesses with branching mechanisms of infinite variance.
    There are also many limiting theory for branching processes and branching Markov processes with branching mechanisms of infinite second moments.
    Heyde \cite{Heyde1971Some} established a central limit type  theorem for Galton-Watson process 
when the offspring distribution
    %belongs to the domain of a stable law of index $\alpha\in (1, 2]$, 
    belongs to the domain of attraction of a stable law of index $\alpha\in (1, 2]$,
    and   proved that the limit law is  a stable law. Similar results  for supercritical multi-type Galton-Watson processes and supercritical  continuous time branching processes,  
under some $p$-th ($p\in(1,2]$) moment condition on the offspring distribution,
    were given in Asmussen \cite{Asmussen76Convergence}.
    Recently,   Marks and Milo\'s \cite{MarksMilos2018CLT}
    considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law. 
    %They established some central limit theorems in small and critical branching rate regimes, but they did not prove any central limit theorem type result in the large branching rate regime.
    They established some central limit theorems in small and critical branching rate regimes, but they did not prove any central limit theorem type result in the large branching rate regime.
%NEW ADDED
    We also mention here that very recently \cite{IksanovKoleskoMeiners2018Stable-like} considered the stable fluctuations of Biggins' martingales in the context of branching random walks and \cite{RenSongSun2018Limit} considered the asymptotic behavior of a class of critical superprocesses with spatially dependent stable branching.
%END NEW ADDED

%NEW ADDED
    As far as we know, this paper is the first one in the literature on establishing CLT for supercritical superprocesses without the second moment condition.
%END added
%DELETED
    %In this paper, we consider a class of super-OU processes with a general stable branching mechanism.
    %For small and critical branching rate regimes, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MarksMilos2018CLT}.
    %For large branching rate regime, we not only prove an almost sure convergence result as in \cite{MarksMilos2018CLT}, we also prove a central limit theorem type result.
%END DELETED

%DELETED    
    %For recent works on limit results (strong law of large numbers and central limit theorems) for branching diffusions and general branching Markov processes, we refer to \cite{BansayeDelmasMarsalleTran2011Limit, ChenRenSongZhang2017Law, EnglanderHarrisKyprianou2010Strong, GrubelKabluchko2016A-functional, RenSongZhang2015Central} and references there in.
%END DELETED
